---
title: "R01 Example Graphics"
author: "Ou Zhang"
date: "4/22/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r load-package, include = FALSE}
packages <- c("tidyverse","tseries","fpp3","fpp","forecast")
packages <- lapply(packages, FUN = function(x) {
    if (!require(x, character.only = TRUE)) {
        install.packages(x)
        library(x, character.only = TRUE)
    }
})

library(fpp)

```

The goal is to visualize what is time-series data.

`fpp` package is a collection of the data for "Forecasting: principles and practice".

[Forecasting: Principles and Practice](https://otexts.com/fpp3/) is a great textbook written by Rob J Hyndman and George Athanasopoulos.

* Data -`melsyd` is the Total weekly air passenger numbers on Ansett airline flights between
Melbourne and Sydney, 1987–1992.

* Data -`a10` is the Monthly anti-diabetic drug sales in Australia from 1992 to 2008.

* Data -`fuel` is the Fuel economy data on 2009 vehicles in the US.

```{r simple forecast}

# USE data from `fpp`.
# Data- melsyd is the Total weekly air passenger numbers on Ansett airline flights between
# Melbourne and Sydney, 1987–1992.
plot(melsyd[,"Economy.Class"],
     main = "Economy class passengers: Melbourne-Sydney",
     xlab = "Year", ylab = "Thousands")

# Monthly anti-diabetic drug sales in Australia from 1992 to 2008
plot(a10, ylab = "$ million", xlab = "Antidiabetic drug sales")

# create season plot 
seasonplot(a10, ylab = "$ million", xlab = "year",
           main="Seasonal plot: antidiabetic drug sales",
           year.labels=TRUE, year.labels.left=TRUE, col=1:20, pch=19)

# month plot
monthplot(a10,ylab="$ million", xlab="Year", xaxt="n",
          main="seasonal deviation plot: antidiabetic drug sales")
axis(1, at=1:12, labels=month.abb,cex=0.8) # adding x-label

# explore the relationship between mpg and carborn footprint.
# 'Jitter’ function (Add Noise) to Numbers
# Add a small amount of noise to a numeric vector.
plot(jitter(fuel[,5]), jitter(fuel[,8]), xlab="City mpg", ylab="Carbon footprint")

# check the correlation between these variables-"Litres"  "City"    "Highway" "Carbon" 
pairs(fuel[,-c(1:2,4,7)],pch=19)


```


