---
title: "Forecast Accuracy"
author: "Ou Zhang"
date: "4/24/2022"
output: html_document
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```


# Forecast Error Statistics

## Forecast Error

$$e_{i} = y_{i} - \hat{y}_{i}$$

## Scale Dependent Measures of Error

<center>

Mean absolute error: MAE = $mean(|e_{i}|)$    


Root mean square error: RMSE = $\sqrt{mean(e^2_{i})}$

</center>


## Scale Independent Error, Percentage Errors

$$ p_{i} = 100\times e_{i}/y_{i}$$
<center>
Mean absolute percentage error: MAPE = $mean(|p_{i}|)$
</center>


## Scale Independent Error, Scaled Errors (Hyndman and Koehler 2006)

### Mean Absolute Scaled Error - MASE


```{r load-package, include = FALSE}
packages <- c(
  "tidyverse", "tseries", "fpp3", "fpp", "forecast",
  "corrplot", "PerformanceAnalytics"
)
packages <- lapply(packages, FUN = function(x) {
  if (!require(x, character.only = TRUE)) {
    install.packages(x)
    library(x, character.only = TRUE)
  }
})

library(fpp)
```

We use example data from R02.rmd, and use `beer2` as the training set.
Then, we create a new dataset-`beer3` as the test set to check the forecast accuracy.

Usually, we compare **RMSE**, **MAPE**, and **MASE** across different methods' accuracy coefficient.


```{r seasonal example, warning=FALSE}

# Example from R02.

# Use beer2 as a training set
beer2 <- window(ausbeer, start = 1992, end = 2006 - .1)

beerfit1 <- meanf(beer2, h = 11)
beerfit2 <- naive(beer2, h = 11)
beerfit3 <- snaive(beer2, h = 11)

plot(beerfit1,
  plot.conf = FALSE,
  main = "Forecasts for quarterly beer production"
)
lines(beerfit2$mean, col = 2)
lines(beerfit3$mean, col = 3)
legend("topright",
  lty = 1, col = c(4, 2, 3),
  legend = c("Mean method", "Naive method", "Season naive method")
)


# accuracy
# beer3 is used as a test set.
beer3 <- window(ausbeer, start = 2006)

accuracy(beerfit1, beer3)
accuracy(beerfit2, beer3)
accuracy(beerfit3, beer3)
```

Let's look at some non-seasonal example:

```{r nonseasonal example, warning = FALSE}


# stock data-dow jones
dj2 <- window(dj, end = 250)

plot(dj2,
  main = "Dow Jones Index (daily ending 15 July 94)",
  ylab = "", xlab = "Day", xlim = c(2, 290)
)
lines(meanf(dj2, h = 42)$mean, col = 4)
lines(rwf(dj2, h = 42)$mean, col = 2)
lines(rwf(dj2, drift = TRUE, h = 42)$mean, col = 3)
legend("topleft",
  lty = 1, col = c(4, 2, 3),
  legend = c("Mean method", "Naive method", "Drift method")
)

# create test dataset

dj3 <- window(dj, start = 251)
accuracy(meanf(dj2, h = 42), dj3)
accuracy(rwf(dj2, h = 42), dj3)
accuracy(rwf(dj2, drift = TRUE, h = 42), dj3)
```
