---
title: "X11 Decomposition"
author: "Ou Zhang"
date: "4/24/2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# X11 Decomposition

* Originated - US Census Bureau and Statistics Canada
* Based on classical decomposition, but includes many extra steps and features
* In particular, trend-cycle estimates are available for all observations including the end points
* seasonal component is allowed to vary slowly over time
* also has some sophisticated methods for handling trading day variation, holiday effects and the effects of known predictors
* both additive and multiplicative decomposition
* process is entirely automatic 
* highly robust to outliers and level shifts in the time series.



```{r load-package, include = FALSE}
packages <- c(
  "tidyverse", "tseries", "fpp3", "fpp","fpp2", "forecast",
  "corrplot", "PerformanceAnalytics","seasonal")
packages <- lapply(packages, FUN = function(x) {
  if (!require(x, character.only = TRUE)) {
    install.packages(x)
    library(x, character.only = TRUE)
  }
})

library(fpp2)

```
Somehow, the `X11` keyword on the command `seas` from the `seasonal` package doesent' work. 
It gives an error meesage below:

> Error in x13_import(iofile, x = list[["x"]], na.action = na.action, out = out) : no output has been generated. 

For the illustration purpose, I comment out `seas` line below.



```{r example}

library(seasonal)

# decompose command
elecequip %>% 
    decompose(type = "multiplicative") %>% 
    autoplot() + xlab("Year") +
    ggtitle("Classicial equipment index")

# x11
# elecequip %>% seas(elecequip, x11="") -> fit
# autoplot(fit) + ggtitle("X11 decomposition of electrical equipment index")

```

